Computing astrophysical inferences with diffusive nested sampling

### 2014-01-14 ms.tex
Slight amount of writing

In many subfields within astronomy, Bayesian inference has (rightfully)
become the dominant framework for analysing data and quantifying the
plausibility of hypotheses about the universe.

@@

\section{Diffusive Nested Sampling}
DNS is essentially just the Metropolis algorithm. However, instead of the
target distribution being the posterior $p(\pars|\data)$, it is the mixture
of constrained priors.

@@

We have been using the following subjective procedure. Later we give two
interpretations of this procedure which may lead the way to less subjective
approaches.
Using DNS we explore the mixture of constrained priors.
\begin{eqnarray}
p_{\rm DNS}(\theta) &=& \frac{1}{n}\sum_{i=1}^n
\frac{p(\theta)\mathds{1}\left[L(\theta) > L^*_i\right]}{X_i}
\end{eqnarray}
where $X_i \approx e^{-i}$ by construction.

>>>>

In many subfields within astronomy, Bayesian inference has (rightfully)
become the dominant framework for analysing data and quantifying the
plausibility of hypotheses about the universe \citep[e.g.][]{refs}.

@@

\section{Diffusive Nested Sampling}
DNS is essentially just the Metropolis algorithm. However, instead of the
target distribution being the posterior $p(\pars|\data)$, the algorithm
constructs and then samples a ``mixture of constrained priors'':

\begin{eqnarray}
p_{\rm DNS}(\theta) &=& \frac{1}{n}\sum_{i=1}^n
\frac{p(\theta)\mathds{1}\left[L(\theta) > L^*_i\right]}{X_i}
\end{eqnarray}

The zeroth component of this mixture is just the prior $p(\pars)$. The first
mixture component is the prior, but restricted to the domain where the
likelihood is greater than a threshold $L^*_1$. The second mixture component
is the prior, but restricted to the domain where the likelihood is above
$L^*_2$. The likelihood thresholds $\{ L^*_i \}$ are chosen so each
successive constrained prior occupies approximately $\exp(-1)$ times as much
prior mass (``volume'') as the previous constrained prior.

@@

We have been using the following subjective procedure. Later we give two
interpretations of this procedure which may lead the way to less subjective
approaches.
Using DNS we explore the mixture of constrained priors.

where $X_i \approx e^{-i}$ by construction.
